\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{geometry}
\geometry{margin=1in}

\title{Requirements for IMDb-like Movie Recommendation Project}
\author{AI Generated Requirements}
\date{\today}

\begin{document}
\maketitle

\section{Project goals \& constraints}
\begin{itemize}
  \item Primary goal: a single-repo, monolithic full-stack web app (Next.js) that offers movie discovery, per-movie pages, user accounts, reviews, ratings, and simple recommendations.
  \item Budget constraint: free tiers only (Vercel + Supabase + TMDB). Supabase free DB storage $\sim$500MB \textrightarrow{} avoid storing large media blobs.
  \item Deploy model: CI/CD automatic on GitHub \textrightarrow{} Vercel production.
\end{itemize}

\section{Actors (users \& roles)}
\begin{itemize}
  \item Anonymous visitor (browse, search, see SSR pages)
  \item Registered user (all visitor actions + post review, rate, like, watchlist)
  \item Admin (manage seeded movie data, moderate reviews — optional for MVP)
\end{itemize}

\section{High-level user stories (prioritized)}
\begin{enumerate}
  \item Visitor can see a homepage with recommendations, popular lists and a search box.
  \item Visitor can view an SSR movie page with metadata, cast (if available), ratings and reviews.
  \item User can sign up / log in (Supabase Auth).
  \item User can post/edit/delete their reviews and rate movies.
  \item User can add/remove movies to a watchlist and mark as watched.
  \item User can like other users’ reviews.
  \item User gets personalized recommendations (exclude movies already watched).
  \item Admin can re-seed or refresh TMDB metadata (script).
\end{enumerate}

\section{Functional requirements}
\subsection{Pages \& navigation}
\begin{itemize}
  \item \texttt{/} — Home (SSR): top N recommendations, trending, genres, quick search.
  \item \texttt{/movies/[id]} — Movie page (SSR): title, release date, runtime, genres, poster, overview, average rating, reviews list, action UI (rate, add to watchlist).
  \item \texttt{/users/[id]} — User profile (SSR): public reviews, stats (reviews count, avg rating).
  \item \texttt{/reviews/[id]} — Review page (SSR optional).
  \item Server routes (Next.js API routes) for mutations (\texttt{POST /api/reviews}, \texttt{POST /api/ratings}, \texttt{PATCH /api/watchlist}, etc.).
\end{itemize}

\subsection{Authentication \& profile}
Use Supabase Auth (email/password) for login/signup and session management (JWT). Profile table stored in DB to hold display name, avatar URL and preferences.

\subsection{Movies metadata \& TMDB integration}
\begin{itemize}
  \item Seed script pulls a curated set of movies (e.g., top 500) from TMDB and stores minimal metadata.
  \item For missing pages, fetch from TMDB on demand and persist.
  \item Do \textbf{not} store poster images in Supabase; use TMDB image URLs.
\end{itemize}

\subsection{Reviews / Ratings / Likes / Watchlist}
\begin{itemize}
  \item Reviews: create/edit/delete by author only, rating 1--10.
  \item Ratings: separate entity, unique per user/movie.
  \item Likes: unique per user/review.
  \item Watchlist: status enum \{want\_to\_watch, watching, watched\}.
\end{itemize}

\subsection{Search \& filters}
\begin{itemize}
  \item Search by title and overview.
  \item Filters: genre, year, runtime range, sort by popularity, release date, average rating, or most reviewed.
  \item Pagination with page/limit or cursor.
\end{itemize}

\subsection{Recommendations (MVP)}
Simple hybrid: combine popularity (TMDB) + content-based similarity (genres/keywords) + exclude watched movies.

\section{Non-functional requirements}
\begin{itemize}
  \item SSR for SEO.
  \item WCAG AA accessibility.
  \item Edge caching; throttle API routes; avoid image storage.
  \item DB indexing for scalability.
  \item Security: RLS, input validation, CSRF protection.
  \item Privacy: user can delete account and personal data.
\end{itemize}

\section{Data model}
Provide a Prisma schema defining \texttt{User}, \texttt{Movie}, \texttt{Genre}, \texttt{Review}, \texttt{Rating}, \texttt{Watchlist}, and \texttt{Like} tables with appropriate relations and unique constraints.

\section{API surface}
All write endpoints require Supabase JWT authentication.  
Examples:
\begin{itemize}
  \item \texttt{GET /api/movies?query=\&genres=\&page=\&sort=} — list movies.
  \item \texttt{GET /api/movies/:tmdbId} — details + ratings + reviews.
  \item \texttt{POST /api/reviews} — create review.
  \item \texttt{PATCH /api/reviews/:id}, \texttt{DELETE /api/reviews/:id}.
  \item \texttt{POST /api/ratings} — upsert rating.
  \item \texttt{POST /api/watchlist} — manage watchlist.
  \item \texttt{GET /api/recommendations?userId=\&size=10} — personalized recommendations.
\end{itemize}

\section{Security \& privacy}
Row Level Security enforced, input sanitization, JWT verification, and rate limiting (e.g., 60 req/min per IP for mutations).

\section{Testing \& CI/CD}
Unit, component, and end-to-end tests (Jest, React Testing Library, Playwright).  
GitHub Actions pipeline: lint, type-check, tests, deploy to Vercel.

\section{Monitoring \& logging}
Use Sentry, Supabase logs, and a simple analytics table for DAU/MAU metrics.

\section{Acceptance criteria}
\begin{itemize}
  \item User signup creates profile.
  \item Movie page returns correct metadata and average rating.
  \item Authenticated user can create/edit/delete their own review.
  \item Recommendations exclude watched movies.
  \item Seed script populates DB with at least 100 movies.
\end{itemize}

\section{Roadmap}
\textbf{MVP}: Auth, seeded TMDB data, movie SSR page, reviews/ratings CRUD, watchlist, simple recommendations, CI + tests + deploy.  
\textbf{Next}: Likes, user profiles, pagination improvements, full-text search, analytics, stronger privacy controls.  
\textbf{Later}: Collaborative filtering, social features, admin moderation UI, image uploads.

\section{Risks \& mitigations}
\begin{itemize}
  \item Supabase 500MB limit: store metadata only, purge old logs.
  \item TMDB rate limits: cache aggressively, seed curated set.
  \item Vercel free limits: monitor bandwidth, use ISR for high-traffic pages.
\end{itemize}

\section{Deliverables}
README with architecture diagram, schema.prisma and migrations, seed script, API documentation, test reports, and Vercel deployment link.

\end{document}
