\documentclass{article}
\usepackage[margin=1in]{geometry}
\usepackage{array}
\usepackage{longtable}
\usepackage{lscape}

\begin{document}

\renewcommand{\arraystretch}{1.2}
\setlength{\tabcolsep}{6pt}

\begin{longtable}{|p{2cm}|p{13cm}|}
\hline
\textbf{FR ID} & \textbf{Functional Requirement} \\ \hline
\endfirsthead
\hline
\textbf{FR ID} & \textbf{Functional Requirement} \\ \hline
\endhead

FR1 & The system must support registration, login, and basic user profile management. \\ \hline
FR2 & The system must be able to manage their profile (view and edit personal information). \\ \hline
FR3 & The system must allow navigation through a movie catalog with details (title, genre, description, average rating). \\ \hline
FR4 & The system must include search functionality by title. \\ \hline
FR5 & The system must allow users to rate items with 0.5--5 stars. \\ \hline
FR6 & The system must generate recommendations based on rating history or popularity. \\ \hline
FR7 & The system must provide filtering options through the movie catalog (e.g., by genre, rating, director, year). \\ \hline
FR8 & The system must provide ordering options through the movie catalog (e.g., by rating, release date, alphabetical, popularity). \\ \hline
FR9 & The system must store and manage user search history. \\ \hline
FR10 & The system must provide a backend with API for interaction between frontend and database. \\ \hline
FR11 & The system must use a database to store users, movies, ratings and recommendations. \\ \hline
FR12 & The system must be accessible via web. \\ \hline
FR13 & The system must have a basic configuration for automation of builds, tests, and deployment. \\ \hline
FR14 & The system must be deployed in a cloud. \\ \hline

\end{longtable}


\end{document}
